### 2011-01-02 docs/slides/mimicry.tex
Additional slides.

	\begin{itemize}
		\item 
	\end{itemize}	
}

@@

	\begin{itemize}
		\item 
	\end{itemize}
}

>>>>

	\begin{itemize}
		\item Examine the local butterfly fauna in any area of the world to find, between all the aposomatic species, only a limited number of different patterns, normally far smaller than the number of species.
		\item Each cluster of species, all sharing a common pattern is termed as Mullerina mimicry ring.
		\item Consider all the rain forest in South and Central America, most of the long winged butterflies (ithomiids, danaids and heliconids) belong to one of only five different rings.
	\end{itemize}	
}

@@

	Turner's theory of Mimicry Ring Formation, takes into account
	\begin{itemize}
		\item the level of protection of different rings
		\item their difference in phenotypic warning patterns.
	\end{itemize}

	Varying these two parameters give different formation of mimicry rings:
	\begin{itemize}
		\item Similar pattern in one habitat:
			\begin{itemize}
				\item Similar enough that the envelop of protection in one provides protection to the other.
				\item \textbf{Result:} Natural protection of mutual convergence.
			\end{itemize}
		\item Very dissimilar patterns:
			\begin{itemize}
				\item Envelop of protection do not overlap. Predator consuming one will not mistake of the other pattern.
				\item \textbf{Result:} No convergence, two patterns will remain distinct.
			\end{itemize}
		\item Mutation:
			\begin{itemize}
				\item Mutation can lead one species into the envelop of protection of another species. 
				\item \textbf{Result:} Gradual convergence of one pattern with another.
			\end{itemize}
	\end{itemize}
}
